---
title: "Trichoderma Antagonism Assays"
author: "Aaron Onufrak"
date: "2023-03-22"
output: rmdformats::downcute
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Packages

```{r,warning=FALSE,message=FALSE}
library(drc)
library(tidyr)
library(ggplot2)
library(ggpubr)
library(car)
library(data.table)
```

# Custom Functions

## Function 01: Percent Inhibition tabulator

This function is used to calculate percent inhibition from a data frame that contains the colony area information for multiple isolates across multiple treatments. The function takes the following arguments:

1. **df**: The data frame (in wide format) that contains the isolate names and the treatments. 
2. **isolate_names**: This is the list of trichoderma isolates used in the juglone assays. If these are present then the function will tabulate percent inhibition for the juglone assays. 
3. **concentration_list**: This is the list of metabolite percentages. If these are present then the function will tabulate percent inhibition for the poison agar assays. 

```{r}
percent_inhibition_tabulator<-function(df,isolate_names=NULL,concentration_list=NULL){
  if(is.null(concentration_list)==TRUE){
  percent_inhibition_frames<-data.frame()
for(i in 1:length(isolate_names)){
  regexp<-paste0("\\b",isolate_names[[i]],"\\b") # This will make it so that grep only selects the exact isolate name
  individ_isolate_data<-df[grep(regexp,df$Isolate),] # Subsetting so that only a single isolate is being considered
  isolate_zero_avg<-mean(individ_isolate_data$`0`,na.rm = TRUE) # Calculating the mean colony area for the selected isolate
  percent_inhibition_isolate<-100*((isolate_zero_avg-Filter(x=individ_isolate_data,f=is.numeric))/isolate_zero_avg) # Calculating percent inhibition
  percent_inhibition_isolate_frame<-data.frame(isolate=isolate_names[[i]],replicate=individ_isolate_data["Replicate"], percent_inhibition_isolate) # Creating new data frame
  colnames(percent_inhibition_isolate_frame)<-sub("X","",colnames(percent_inhibition_isolate_frame)) # Removing X's that show up in new column names
  percent_inhibition_isolate_frame_long<-gather(percent_inhibition_isolate_frame,Concentration,percent_inhibition,3:7)
  percent_inhibition_frames<-rbind(percent_inhibition_frames,percent_inhibition_isolate_frame_long)
}
  return(percent_inhibition_frames)
  # this will shunt into the version for the trichoderma poison agar analyses
} else {
  poison_inhibition_frames<-data.frame()
for(i in 1:length(poison_concentrations)){
  poison_inhibition_by_gm_iso<-df[grep(concentration_list[[i]], df$Percentage),] # This will grep the metabolite percentage 
  isolate_zero_avg<-mean(poison_inhibition_by_gm_iso$PDA,na.rm = TRUE) # This will select the PDA treatment control for mean calculation
  percent_inhibition_isolate<-((isolate_zero_avg-Filter(x=poison_inhibition_by_gm_iso,is.numeric))/isolate_zero_avg)*100 # Calculates the percent inhibition selection only numeric columns in the data frame. 
  percent_inhibition_isolate_df<-data.frame(replicate=poison_inhibition_by_gm_iso$Replicate,Percentage=poison_inhibition_by_gm_iso$Percentage,Isolate=poison_inhibition_by_gm_iso$Isolate,percent_inhibition_isolate)
  percent_inhibition_isolate_frame_long<-gather(percent_inhibition_isolate_df,treatment,percent_inhibition,4:length(percent_inhibition_isolate_df))
  poison_inhibition_frames<-rbind(poison_inhibition_frames,percent_inhibition_isolate_frame_long)
}
  return(poison_inhibition_frames)
}
}
```

# Outline
The following code details the analyses performed for the following laboratory assays:

1. *Beauveria bassiana* and *Trichoderma* spp. juglone assays. 
2. *Trichoderma* spp. and *Geosmithia morbida* dual-plate antagonism assays. 
3. *Trichoderma* spp. metabolite assays against *Geosmithia morbida*


# Part 01: Juglone assays

## Data Import

Importing data into R. The following two data frames are used for the analyses:

1. **b_bassiana_juglone_responses.txt**: contain the colony areas of *B. bassiana* strain GHA to juglone 3 days after inoculation. 
2. **trichoderma_juglone_responses.txt**: contain the colony areas of the 15 *Trichoderma* isolates to juglone. 

All colony areas used in the study were measured using [ImageJ](https://imagej.net/ij/). 

```{r}
# Importing Beauveria colony area
beauveria.juglone<-read.table("/Users/aarononfurak/Library/CloudStorage/GoogleDrive-onufrak.aaron@gmail.com/My Drive/utk_project/trichoderma_antagonism_manuscript/raw_data/b_bassiana_juglone_responses.txt",sep='\t',header=TRUE)

# Importing Trichoderma colony area data
trichoderma.juglone<-read.table("/Users/aarononfurak/Library/CloudStorage/GoogleDrive-onufrak.aaron@gmail.com/My Drive/utk_project/trichoderma_antagonism_manuscript/raw_data/trichoderma_juglone_responses.txt",sep='\t',header=TRUE)
```

## Part 01.1: Beauveria juglone data analyses

Below I do all of the statistical analyses for *B. bassiana* strain GHA to juglone. The procedure goes as follows:

1. Calculate the mean area of colonies grown on the now juglone control.
2. Use the mean to calculate percent growth inhibition for the colonies on all of the juglone concentrations. We also include in our analyses the the negative control plates to account for the amount of variation in growth at the negative control. 
3. Conduct a two-way ANOVA to detect significant differences in percent growth inhibition by juglone concentrations. 

```{r}
# Changing concentration to a factor
beauveria.juglone$Concentration<-as.factor(beauveria.juglone$Concentration)

# Omitting NAs from beauveria data
beauveria.juglone_no_na<-na.omit(beauveria.juglone)

# Converting table to wide format
beauveria.juglone_no_na_wide<-spread(beauveria.juglone_no_na,Concentration,area)

# Converting replicate to a factor so that it is not treated numerically.  
beauveria.juglone_no_na_wide$Replicate<-as.character(beauveria.juglone_no_na_wide$Replicate)

# Calculating average of acetone control. Setting na.rm to true to remove NA entries. 
beauveria.juglone_no_na_control_average<-mean(beauveria.juglone_no_na_wide$`0`,na.rm = TRUE)

# Calculating percent inhibition of colony growth
beauveria.juglone_no_na_control_average_percent_inhibition<-100*((beauveria.juglone_no_na_control_average-Filter(x=beauveria.juglone_no_na_wide,f=is.numeric))/beauveria.juglone_no_na_control_average)

# Converting table from wide format to long
beauveria.juglone_no_na_control_average_percent_inhibition_long<-gather(beauveria.juglone_no_na_control_average_percent_inhibition,Concentration,percent_inhibition,1:5)

# Sanity check to make sure number of rows is correct after omitting NAs
nrow(na.omit(beauveria.juglone_no_na_control_average_percent_inhibition_long))

# Removing NA values from the table
beauveria.juglone_no_na_control_average_percent_inhibition_long<-na.omit(beauveria.juglone_no_na_control_average_percent_inhibition_long)

# Converting concentration to a factor
beauveria.juglone_no_na_control_average_percent_inhibition_long$Concentration<-as.factor(beauveria.juglone_no_na_control_average_percent_inhibition_long$Concentration)

# Conducting ANOVA on Beauveria data 
beauveria.juglone_percent_inhibition_aov<-aov(percent_inhibition~Concentration,beauveria.juglone_no_na_control_average_percent_inhibition_long,)

# Assessing model assumpions
par(mfrow=c(2,2))
plot(beauveria.juglone_percent_inhibition_aov)

# Doing a type III ANOVA to account for differences in sample sizes as a result of plug dislodging. 
Anova(beauveria.juglone_percent_inhibition_aov,type="III")

# Using tukeys post-hoc test to detect significant pair-wise differences
beauveria.juglone_tukey_results<-TukeyHSD(beauveria.juglone_percent_inhibition_aov)
beauveria.juglone_tukey_results 

# Plotting results in ggplot
beauveria_plot<-ggplot(data=beauveria.juglone_no_na_control_average_percent_inhibition_long,aes(x=Concentration,y=percent_inhibition,fill=Concentration))+
geom_boxplot(outlier.shape=NA)+
  geom_jitter()+
  geom_hline(yintercept = c(0,50),linetype=2)+
  theme(panel.grid=element_blank(),panel.background = element_blank(),panel.border = element_rect(fill=NA),strip.background = element_blank())+
  scale_y_continuous(limits=c(-100,100),breaks=c(-100,-75,-50,-25,0,25,50,75,100))+
  geom_text(data=NULL,aes(x=1,y=100,label="A"),inherit.aes = FALSE)+
  geom_text(data=NULL,aes(x=2,y=100,label="B"),inherit.aes = FALSE)+
  geom_text(data=NULL,aes(x=3,y=100,label="C"),inherit.aes = FALSE)+
  geom_text(data=NULL,aes(x=4,y=100,label="C"),inherit.aes = FALSE)+
  geom_text(data=NULL,aes(x=5,y=100,label="C"),inherit.aes = FALSE)+
  ylab("Percent Inhibition (%)")+
  xlab("Concentration (mg/mL)")

beauveria_plot
```


## Part 01.2: Trichoderma juglone data analyses

Below I do all of the statistical analyses for 15 *Trichodmera* isolates to juglone. The procedure goes as follows:

1. Calculate the mean area of colonies grown on the now juglone control.
2. Use the mean to calculate percent growth inhibition for the colonies on all of the juglone concentrations. We also include in our analyses the the negative control plates to account for the amount of variation in growth at the negative control. 
3. Conduct a two-way ANOVA to detect significant differences in percent growth inhibition by juglone concentrations. 

```{r}
# Determining the number of plugs that fell off of each isolate
nrow(trichoderma.juglone[grep("^[^N].*Gm",trichoderma.juglone$Isolate,invert=TRUE),])
nrow(na.omit(trichoderma.juglone[grep("^[^N].*Gm",trichoderma.juglone$Isolate, invert=TRUE),]))

# Removing NAs
trichoderma.juglone_no.na<-na.omit(trichoderma.juglone)

# Converting the table to wide format
trichoderma.juglone_no.na_wide<-spread(trichoderma.juglone_no.na,Concentration,Area)

trichoderma.juglone_no.na_wide$Replicate<-as.character(trichoderma.juglone_no.na_wide$Replicate)

# Parsing out Trichoderma isolate names
trichoderma.isolate.names<-unique(trichoderma.juglone_no.na_wide$Isolate)

# Calculating percent inhibition on a isolate basis
trichoderma.juglone_inhibition_frames<-percent_inhibition_tabulator(isolate_names=trichoderma.isolate.names,df=trichoderma.juglone_no.na_wide)

# Omitting NAs
trichoderma.juglone_inhibition_frames<-na.omit(trichoderma.juglone_inhibition_frames)

# Converting concentration to a factor
trichoderma.juglone_inhibition_frames$Concentration<-as.factor(trichoderma.juglone_inhibition_frames$Concentration)

# Conducting ANOVA
trichoderma.juglone_percent_inhibition_aov<-aov(percent_inhibition~isolate*Concentration,trichoderma.juglone_inhibition_frames)

# Assessing model assumptions
par(mfrow=c(2,2))
plot(trichoderma.juglone_percent_inhibition_aov)

# Determining p-values 
Anova(trichoderma.juglone_percent_inhibition_aov,type="III")
tricho.tukey_results<-TukeyHSD(trichoderma.juglone_percent_inhibition_aov)

# Pulling out post-hoc results per isolate

# NGM36-1
ngm36_1<-tricho.tukey_results$`isolate:Concentration`[grep("NGM36-1.*-NGM36-1.*",row.names(tricho.tukey_results$`isolate:Concentration`)),]
ngm36_1

# Rootshield (AKA KRL-AG2)
rootshield<-tricho.tukey_results$`isolate:Concentration`[grep("RootShield:.*-RootShield:.*",row.names(tricho.tukey_results$`isolate:Concentration`)),]
rootshield

# TN-26
tn1_26<-tricho.tukey_results$`isolate:Concentration`[grep("TN1-26.*-TN1-26.*",row.names(tricho.tukey_results$`isolate:Concentration`)),]
tn1_26

# TN1-2
tn1_2<-tricho.tukey_results$`isolate:Concentration`[grep("TN1-2:.*-TN1-2:.*",row.names(tricho.tukey_results$`isolate:Concentration`)),]
tn1_2

# TN1-4
tn1_4<-tricho.tukey_results$`isolate:Concentration`[grep("TN1-4:.*-TN1-4:.*",row.names(tricho.tukey_results$`isolate:Concentration`)),]
tn1_4

# TN1-66
tn1_66<-tricho.tukey_results$`isolate:Concentration`[grep("TN1-66:.*-TN1-66:.*",row.names(tricho.tukey_results$`isolate:Concentration`)),]
tn1_66

#TN2-51
tn2_51<-tricho.tukey_results$`isolate:Concentration`[grep("TN2-51:.*-TN2-51:.*",row.names(tricho.tukey_results$`isolate:Concentration`)),]
tn2_51

# TN3-2
tn3_2<-tricho.tukey_results$`isolate:Concentration`[grep("TN3-2:.*-TN3-2:.*",row.names(tricho.tukey_results$`isolate:Concentration`)),]
tn3_2

# TN3-21
tn3_21<-tricho.tukey_results$`isolate:Concentration`[grep("TN3-21:.*-TN3-21:.*",row.names(tricho.tukey_results$`isolate:Concentration`)),]
tn3_21

# TN3-49
tn3_49<-tricho.tukey_results$`isolate:Concentration`[grep("TN3-49:.*-TN3-49:.*",row.names(tricho.tukey_results$`isolate:Concentration`)),]
tn3_49

# TN3-61
tn3_61<-tricho.tukey_results$`isolate:Concentration`[grep("TN3-61:.*-TN3-61:.*",row.names(tricho.tukey_results$`isolate:Concentration`)),]
tn3_61

# TN4-40
tn4_40<-tricho.tukey_results$`isolate:Concentration`[grep("TN4-40:.*-TN4-40:.*",row.names(tricho.tukey_results$`isolate:Concentration`)),]
tn4_40

# TN4-47
tn4_47<-tricho.tukey_results$`isolate:Concentration`[grep("TN4-47:.*-TN4-47:.*",row.names(tricho.tukey_results$`isolate:Concentration`)),]
tn4_47

# TN5-34
tn5_34<-tricho.tukey_results$`isolate:Concentration`[grep("TN5-34:.*-TN5-34:.*",row.names(tricho.tukey_results$`isolate:Concentration`)),]
tn5_34

# TN5-9
tn5_9<-tricho.tukey_results$`isolate:Concentration`[grep("TN5-9:.*-TN5-9:.*",row.names(tricho.tukey_results$`isolate:Concentration`)),]
tn5_9

# Creating a data frame that includes the percent inhibition for B. bassiana that will be merged into the Trichoderma data frame for plotting.
beauveria.juglone_no_na_control_average_percent_inhibition_long_df<-data.frame(isolate=rep("GHA",times=nrow(beauveria.juglone_no_na_control_average_percent_inhibition_long)),beauveria.juglone_no_na_control_average_percent_inhibition_long)

# Merging the B. bassiana data frame in the Trichoderma frame
beauveria.trichoderma.juglone_inhibition_frames<-rbind(beauveria.juglone_no_na_control_average_percent_inhibition_long_df,trichoderma.juglone_inhibition_frames[,grep("Replicate",colnames(trichoderma.juglone_inhibition_frames),invert=TRUE)])

# Changing the name of RootShield to KRL-AG2 for consistency with the manuscript
beauveria.trichoderma.juglone_inhibition_frames$isolate<-sub("RootShield","KRL-AG2",beauveria.trichoderma.juglone_inhibition_frames$isolate)

# Importing a dataframe that contains the significance lettering based on the above tukey tests to add to ggplot
tricho_juglone_sig_codes<-read.table("/Users/aarononfurak/Library/CloudStorage/GoogleDrive-onufrak.aaron@gmail.com/My Drive/utk_project/trichoderma_antagonism_manuscript/raw_data/trichoderma_sig_codes.txt",header=TRUE,sep='\t')

# Converting concentration to factor
tricho_juglone_sig_codes$Concentration<-as.factor(tricho_juglone_sig_codes$Concentration)

# Plotting data in ggplot
juglone_summaries<-ggplot(data=beauveria.trichoderma.juglone_inhibition_frames,aes(x=Concentration,y=percent_inhibition,fill=Concentration))+
geom_boxplot(outlier.shape=NA)+
  geom_jitter()+
  facet_wrap(.~isolate,nrow = 4,ncol=4)+
  geom_hline(yintercept = c(0,50),linetype=2)+
  theme(panel.grid=element_blank(),panel.background = element_blank(),panel.border = element_rect(fill=NA),strip.background = element_blank())+
 geom_text(data=tricho_juglone_sig_codes,aes(x=Concentration,y=110,label=Code),inherit.aes = FALSE)+
  scale_y_continuous(limits=c(-50,110),breaks=c(-50,-25,0,25,50,75,100))+
  ylab("Percent Inhibition (%)")+
  xlab("Concentration (mg/mL)")

juglone_summaries

#ggsave("/Users/aarononfurak/Library/CloudStorage/GoogleDrive-onufrak.aaron@gmail.com/My Drive/utk_project/trichoderma_antagonism_manuscript/manuscript_versions/manuscript_biocontrol_journal/figures/figure_03.eps",juglone_summaries,dpi = 1200,height=12,width=12)

```

# Part 02: Dual-plate Antagonism Assays

## Data Import

Below I import the following data frames:

1. **dual_plate_trial_01.txt**: Contains the antagonism ratings for the first trial of dual-plate assays.
2. **dual_plate_trial_02.txt**: Contains the antagonism ratings for the second trial of dual-plate assays. 

```{r}
# Loading in first trial of dual plate assays
dual_plate_trial_1<-read.table("/Users/aarononfurak/Library/CloudStorage/GoogleDrive-onufrak.aaron@gmail.com/My Drive/utk_project/trichoderma_antagonism_manuscript/raw_data/dual_plate_trial_01.txt",header=TRUE,sep='\t')

# Loading in second trial of dual plate assays
dual_plate_trial_2<-read.table("/Users/aarononfurak/Library/CloudStorage/GoogleDrive-onufrak.aaron@gmail.com/My Drive/utk_project/trichoderma_antagonism_manuscript/raw_data/dual_plate_trial_02.txt",header=TRUE,sep='\t')
```

## Part 02.1: Trial 1 of Dual-Plate Assays

Below I plot the results for the first trial of dual-plate assays. This trial includes 15 different isolates of *Trichoderma* originally recovered in [Gazis et al. 2018](https://www.fs.usda.gov/psw/publications/seybold/psw_2018_seybold002_gazis.pdf).

```{r,warning=FALSE,message=FALSE}
# Changing name of rootshield isolate for consistency with manuscript
dual_plate_trial_1$Isolate<-sub("Rootshield","KRL-AG2",dual_plate_trial_1$Isolate)

# Plotting data in ggplot
dual_plate_round_1<-ggplot(data=dual_plate_trial_1,aes(x=Rating))+
 geom_histogram(color="black",binwidth = 0.5)+
  geom_vline(xintercept = 2.5,linetype=2,color="red")+
  facet_wrap(.~Isolate,scales="free_x",nrow =3 ,ncol=5)+
    theme(panel.grid=element_blank(),panel.background = element_blank(),panel.border = element_rect(fill=NA),strip.background = element_blank())+
  xlab("Antagonism Ranking")+
  ylab("Count")+
  scale_x_continuous(limits=c(0,5),breaks=c(1,2,3,4))+
  scale_y_continuous(limits=c(0,5),breaks=c(1,2,3,4))+
  coord_flip()

dual_plate_round_1
```

## Part 02.2: Trial 2 of Dual-Plate Assays

Below I plot the results for the second trial of dual-plate assays. This trial includes 6 different isolates of *Trichoderma* and 3 different isolates of *G. morbida*

```{r,warning=FALSE,message=FALSE}
# Adjusting isolate names for consistency
dual_plate_trial_2$GM<-sub("CAGM17-1","CA Gm17-1",dual_plate_trial_2$GM)
dual_plate_trial_2$GM<-sub("ORGM62-3","OR Gm62-3",dual_plate_trial_2$GM)
dual_plate_trial_2$GM<-sub("TNGM17","TN Gm17",dual_plate_trial_2$GM)
dual_plate_trial_2$trichoderma<-sub("RootShield","KRL-AG2",dual_plate_trial_2$trichoderma)

# Plotting data in ggplot
dual_plate_round2<-ggplot(data=dual_plate_trial_2,aes(x=rating,fill=GM))+
  geom_histogram(color="black",binwidth = 0.5)+
 # geom_point(data=dual_plate_trial_2,position=position_dodge(width=0.75),aes(x=GM,y=rating))+
geom_vline(xintercept = 2.5,linetype=2,color="red")+
  facet_wrap(.~trichoderma,scales="free_x")+
    theme(panel.grid=element_blank(),panel.background = element_blank(),panel.border = element_rect(fill=NA),strip.background = element_blank())+
  xlab("Antagonism Ranking")+
  ylab("Count")+
  scale_x_continuous(limits=c(0,5),breaks=c(1,2,3,4))+
  scale_y_continuous(limits=c(0,16),breaks=c(0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15))+
  coord_flip()
  
  dual_plate_round2


dual_plate_assay_plot<-ggarrange(dual_plate_round_1,dual_plate_round2,ncol=1,nrow=2,labels=c("A","B"))
dual_plate_assay_plot

#ggsave("/Users/aarononfurak/Library/CloudStorage/GoogleDrive-onufrak.aaron@gmail.com/My Drive/utk_project/trichoderma_antagonism_manuscript/manuscript_versions/manuscript_biocontrol_journal/figures/figure_04.eps",dual_plate_assay_plot,dpi = 1200,height=8,width=12)

```

# Part 03: Trichoderma Metabolite Assays

Importing data into R. The following data frames are used for the analyses:

1. **colony_area_poison_agar.txt**: contains the colony areas for each *G. morbida* x *Trichoderma* metabolite pairing across all three concentrations. 

```{r}
# Loading in the poison agar data
poison_agar_area<-read.table("/Users/aarononfurak/Library/CloudStorage/GoogleDrive-onufrak.aaron@gmail.com/My Drive/utk_project/trichoderma_antagonism_manuscript/raw_data/colony_area_poison_agar.txt",header=TRUE,sep='\t',na.strings = "NA")
```

## Part 03.1: Trichoderma Metabolite Assays: Data Formatting

```{r}
# Determining numer of samples lost to plug dislodging
nrow(poison_agar_area)
nrow(na.omit(poison_agar_area))

# Converting table to wide format
poison_colony_area_jug_no.na_wide<-spread((poison_agar_area),Treatment,Area)

# Converting replicate to a character so it is not interpreted numerically
poison_colony_area_jug_no.na_wide$Replicate<-as.character(poison_colony_area_jug_no.na_wide$Replicate)

# Converting percentage to a character so it is not interpreted numerically
poison_colony_area_jug_no.na_wide$Percentage<-as.character(poison_colony_area_jug_no.na_wide$Percentage)

# Creating a list of the metabolite concentrations used
poison_concentrations<-unique(poison_colony_area_jug_no.na_wide$Percentage)

# Creating a list of the G. morbida isolates used
gm_isos<-unique(poison_colony_area_jug_no.na_wide$Isolate)

# Creating a list object that consists of individual data frames for each G. morbida isolate
poison_inhibition_frames<-data.frame()
gm_isos_poison_inhibition<-list()
for(x in 1:length(gm_isos)){
  gm_isos_poison<-poison_colony_area_jug_no.na_wide[grep(gm_isos[[x]],poison_colony_area_jug_no.na_wide$Isolate),]
  gm_isos_poison_inhibition<-append(gm_isos_poison_inhibition,list(gm_isos_poison))
}


# Applying the percent inhibition calculator function to the list of colony area data frame by G. morbida isolate
poison_percent_inhibition_list<-lapply(X = gm_isos_poison_inhibition,FUN=percent_inhibition_tabulator,concentration_list = poison_concentrations)


# Removing NA values
poison_percent_inhibition_list<-lapply(poison_percent_inhibition_list,na.omit)

# Binding the data frames stored in the list into a single data frame
poison_percent_inhibition_df<-rbindlist(poison_percent_inhibition_list)

# Creating new columns so that I can split treatments out by unautoclaved and autoclaved treatments

# Creating a column that contains the isolate ID (used single letters to avoid biasing results)
poison_percent_inhibition_df$tricho<-sub("^A|^U","",poison_percent_inhibition_df$treatment)

# Creating a column that contains the heat treatment
poison_percent_inhibition_df$heat<-sub("PDA","Autoclave",sub("^U.","Unautoclave",sub("^A.","Autoclave",poison_percent_inhibition_df$treatment)))

# Updating isoalte names to match manuscript
poison_percent_inhibition_df$Isolate<-sub("CA","CA Gm17-1",sub("TN","TN Gm17",sub("OR","OR Gm62-3",poison_percent_inhibition_df$Isolate)))

# Substituting isolate IDs with the their actual names
poison_percent_inhibition_df$iso_code<-poison_percent_inhibition_df$tricho
poison_percent_inhibition_df$iso_code<-sub("^A","TN3-21",poison_percent_inhibition_df$iso_code)
poison_percent_inhibition_df$iso_code<-sub("^B","TN4-47",poison_percent_inhibition_df$iso_code)
poison_percent_inhibition_df$iso_code<-sub("^C","KRL-AG2",poison_percent_inhibition_df$iso_code)
poison_percent_inhibition_df$iso_code<-sub("^D","TN4-40",poison_percent_inhibition_df$iso_code)
poison_percent_inhibition_df$iso_code<-sub("^E","TN3-61",poison_percent_inhibition_df$iso_code)
poison_percent_inhibition_df$iso_code<-sub("^F","TN1-66",poison_percent_inhibition_df$iso_code)

# Adding percent signs to the end of the percentage values
poison_percent_inhibition_df$Percentage<-sub("0","0%",poison_percent_inhibition_df$Percentage)

# Creating an object for only the autoclaved samples 
poison_percent_inhibition_autoclave<-poison_percent_inhibition_df[grep("Autoclave",poison_percent_inhibition_df$heat),]

# Double checking the number of samples
nrow(poison_percent_inhibition_autoclave)

# Creating an object for only the non-autoclaved samples
poison_percent_inhibition_unautoclave_no_pda<-poison_percent_inhibition_df[grep("Unautoclave",poison_percent_inhibition_df$heat),]
poison_percent_inhibition_unautoclave<-rbind(poison_percent_inhibition_unautoclave_no_pda,poison_percent_inhibition_autoclave[grep("PDA",poison_percent_inhibition_autoclave$tricho),])
```

### Part 03.2 Autoclaved samples

```{r}
# Conducting an ANOVA on the autoclaved samples
poison_anova_auto<-aov(percent_inhibition~tricho*Percentage*Isolate,poison_percent_inhibition_autoclave)

# Checking model assumptions
par(mfrow=c(2,2))
plot(poison_anova_auto)

# Extracting ANOVA results
Anova(poison_anova_auto,type="III")

# Determining pairwise significance using Tukey tests
poison_tukey_results_auto<-TukeyHSD(poison_anova_auto)

# Pulling out the significant results using grep for each metabolite percentage

# 30%
poison_30_auto<-poison_tukey_results_auto$`tricho:Percentage`[grep(".*30.*30.*",row.names(poison_tukey_results_auto$`tricho:Percentage`)),]
poison_30_auto[poison_30_auto[,4]<0.05,]

# 50%
poison_50_auto<-poison_tukey_results_auto$`tricho:Percentage`[grep(".*50.*50.*",row.names(poison_tukey_results_auto$`tricho:Percentage`)),]
poison_50_auto[poison_50_auto[,4]<0.05,]

# 70%
poison_70_auto<-poison_tukey_results_auto$`tricho:Percentage`[grep(".*70.*70.*",row.names(poison_tukey_results_auto$`tricho:Percentage`)),]
poison_70_auto[poison_70_auto[,4]<0.05,]

# Creating a data frame that has all of the significance lettering for ggplot
sig_codes_auto<-data.frame(Percentage=c(rep("30%",7),rep("50%",7),rep("70%",7)),TI=c(rep(c("PDA","TN3-21","TN4-47","KRL-AG2","TN4-40","TN3-61","TN1-66"),3)),sig_code=c("A","A","B","CD","AC","A","D",
                                            "A","BD","C","D","BE","AE","D",
                                            "A","BC","D","BC","BC","B","C"))

# Converting isolate IDs to a factor
poison_percent_inhibition_autoclave$iso_code<-factor(poison_percent_inhibition_autoclave$iso_code,levels=c("PDA","TN3-21","TN4-47","KRL-AG2","TN4-40","TN3-61","TN1-66"))

# Changing RootShield name for consistency with the manuscript
poison_percent_inhibition_autoclave$tricho<-sub("RootShield","KRL-AG2",poison_percent_inhibition_autoclave$tricho)

# Plotting results in ggplot
autoclave_pi<-ggplot(data=poison_percent_inhibition_autoclave,aes(x=iso_code,y=percent_inhibition,fill=iso_code))+
geom_boxplot(outlier.shape=NA)+
  geom_point(position = position_jitterdodge(jitter.width = 0.05),color="black",aes(shape=Isolate))+
  facet_wrap(.~Percentage,nrow = 1,ncol=3)+
  geom_hline(yintercept = c(0,50),linetype=2)+
  theme(panel.grid=element_blank(),panel.background = element_blank(),panel.border = element_rect(fill=NA),strip.background = element_blank())+
  geom_text(data=sig_codes_auto,aes(x=TI,y=105,label=sig_code),inherit.aes = FALSE)+
  scale_x_discrete(labels=c("PDA","TN3-21","TN4-47","KRL-AG2","TN4-40","TN3-61","TN1-66"))+
   guides(fill=guide_legend(title = "Trichoderma spp. Isolate"),shape=guide_legend(title="Geosmithia morbida Isolate"))+
  xlab("Trichoderma spp. Isolate")+
  ylab("Percent Inhibition (%)")
autoclave_pi

```

### Part 03.3 Non-autoclaved samples 

```{r}
# Conducting an ANOVA on the unautoclaved samples
poison_anova_unauto<-aov(percent_inhibition~tricho*Percentage*Isolate,poison_percent_inhibition_unautoclave)

# Checking model assumptions
par(mfrow=c(2,2))
plot(poison_anova_unauto)

# Extracting ANOVA results
Anova(poison_anova_unauto,type="III")

# Determining pairwise significance using Tukey tests
poison_tukey_results_unauto<-TukeyHSD(poison_anova_unauto)

# Pulling out the significant results using grep for each metabolite percentage

# 30%
poison_30_unauto<-poison_tukey_results_unauto$`tricho:Percentage`[grep(".*30.*30.*",row.names(poison_tukey_results_unauto$`tricho:Percentage`)),]
poison_30_unauto[poison_30_unauto[,4]<0.05,]

# 50%
poison_50_unauto<-poison_tukey_results_unauto$`tricho:Percentage`[grep(".*50.*50.*",row.names(poison_tukey_results_unauto$`tricho:Percentage`)),]
poison_50_unauto[poison_50_unauto[,4]<0.05,]

# 70%
poison_70_unauto<-poison_tukey_results_unauto$`tricho:Percentage`[grep(".*70.*70.*",row.names(poison_tukey_results_unauto$`tricho:Percentage`)),]
poison_70_unauto[poison_70_unauto[,4]<0.05,]

# Creating a data frame that has all of the significance lettering for ggplot
sig_codes_unauto<-data.frame(Percentage=c(rep("30%",7),rep("50%",7),rep("70%",7)),TI=c(rep(c("PDA","TN3-21","TN4-47","KRL-AG2","TN4-40","TN3-61","TN1-66"),3)),sig_code=c("A","AB","C","BD","ABD","A","D",
                                                                                                                                           "A","AC","B","CD","C","C","D",
                                                                                                                                           "A","A","B","C","C","A","C"))

# Converting isolate IDs to a factor
poison_percent_inhibition_unautoclave$iso_code<-factor(poison_percent_inhibition_unautoclave$iso_code,levels=c("PDA","TN3-21","TN4-47","KRL-AG2","TN4-40","TN3-61","TN1-66"))

# Changing RootShield name for consistency with the manuscript
poison_percent_inhibition_unautoclave$tricho<-sub("RootShield","KRL-AG2",poison_percent_inhibition_unautoclave$tricho)

# Plotting results in ggplot
unautoclave_pi<-ggplot(data=poison_percent_inhibition_unautoclave,aes(x=iso_code,y=percent_inhibition,fill=iso_code))+
geom_boxplot(outlier.shape=NA)+
  geom_point(position = position_jitterdodge(jitter.width = 0.05),color="black",aes(shape=Isolate))+
  facet_wrap(.~Percentage,nrow = 1,ncol=3)+
  geom_hline(yintercept = c(0,50),linetype=2)+
  theme(panel.grid=element_blank(),panel.background = element_blank(),panel.border = element_rect(fill=NA),strip.background = element_blank(),axis.title.x = element_blank())+
  geom_text(data=sig_codes_unauto,aes(x=TI,y=105,label=sig_code),inherit.aes = FALSE)+
  scale_x_discrete(labels=c("PDA","TN3-21","TN4-47","KRL-AG2","TN4-40","TN3-61","TN1-66"))+
  guides(fill=guide_legend(title = "Trichoderma spp. Isolate"),shape=guide_legend(title="Geosmithia morbida Isolate"))+
   xlab("Trichoderma spp. Isolate")+
  ylab("Percent Inhibition (%)")
unautoclave_pi

metabolite_summary_results<-ggarrange(unautoclave_pi,autoclave_pi,nrow=2,common.legend = TRUE,labels=c("Non-autoclaved","Autoclaved"))
metabolite_summary_results

#ggsave("/Users/aarononfurak/Library/CloudStorage/GoogleDrive-onufrak.aaron@gmail.com/My Drive/utk_project/trichoderma_antagonism_manuscript/manuscript_versions/manuscript_biocontrol_journal/figures/figure_05.eps",metabolite_summary_results,dpi = 1200,height=8,width=14,bg="white")

```

### Part 03.4 Assessing effects of heat treatments

```{r,eval=FALSE}
# Removing the PDA control because it does not receive heat treatment
poison_percent_inhibition_df_no_pda<-poison_percent_inhibition_df[grep("PDA",poison_percent_inhibition_df$tricho,invert=TRUE),]

# Performing ANOVA
autoclave_aov<-aov(percent_inhibition~heat*tricho*Percentage+Isolate*tricho*Percentage,data=poison_percent_inhibition_df_no_pda)

# Assessing model assumptions
par(mfrow=c(2,2))
plot(autoclave_aov)

# Getting ANOVA summaries
Anova(autoclave_aov,type="III")

# Assessing pairwise signficant differences using tukey tests
tukey_heat<-TukeyHSD(autoclave_aov)

tukey_heat_tricho_perce<-as.data.frame(tukey_heat$`heat:tricho:Percentage`)
tukey_heat_tricho_perce_sig<-tukey_heat_tricho_perce[tukey_heat_tricho_perce$`p adj`<0.05,]

# Using grep to look at heat x G. 
tukey_heat_tricho_perce_sig[grep("Unautoclave:A:.*-Autoclave:A:.*",row.names(tukey_heat_tricho_perce_sig)),]
tukey_heat_tricho_perce_sig[grep("Unautoclave:B:.*-Autoclave:B:.*",row.names(tukey_heat_tricho_perce_sig)),]
tukey_heat_tricho_perce_sig[grep("Unautoclave:C:.*-Autoclave:C:.*",row.names(tukey_heat_tricho_perce_sig)),]
tukey_heat_tricho_perce_sig[grep("Unautoclave:D:.*-Autoclave:D:.*",row.names(tukey_heat_tricho_perce_sig)),]
tukey_heat_tricho_perce_sig[grep("Unautoclave:E:.*-Autoclave:E:.*",row.names(tukey_heat_tricho_perce_sig)),]
tukey_heat_tricho_perce_sig[grep("Unautoclave:F:.*-Autoclave:F:.*",row.names(tukey_heat_tricho_perce_sig)),]

# Creating a data frame of significant codings for ggplot
sig_codes_heat_trt<-data.frame(Percentage=c(rep(c("30%","50%","70%"),12)),iso_code=c(rep("KRL-AG2",6),rep("TN1-66",6),rep("TN3-21",6),rep("TN3-61",6),rep("TN4-40",6),rep("TN4-47",6)),sig_code=c(NA,"B",NA,NA,"A",NA,rep(NA,6),NA,NA,"A",NA,NA,"B",rep(NA,18)),heat=rep(c("Autoclave","Unautoclave"),18))

# Plotting data in ggplot
ggplot(data=poison_percent_inhibition_df_no_pda,aes(x=Percentage,y=percent_inhibition,fill=heat))+
geom_boxplot(outlier.shape=NA)+
  geom_point(position = position_jitterdodge(jitter.width = 0.05),color="black",aes(shape=Isolate))+
  facet_wrap(.~iso_code,nrow = 2,ncol=3)+
  geom_hline(yintercept = c(0,50),linetype=2)+
  theme(panel.grid=element_blank(),panel.background = element_blank(),panel.border = element_rect(fill=NA),strip.background = element_blank())+
  guides(fill=guide_legend(title = "Heat Treatment"))+
 geom_text(data=sig_codes_heat_trt,aes(x=Percentage,y=105,label=sig_code,group=heat),position = position_jitterdodge(jitter.width = 0.05))+
  ylab("Percent Inhibition (%)")+
  #geom_segment(data=sig_codes_heat_trt,aes(x=x,xend=xend,y=100,yend=100),inherit.aes = FALSE)+
  xlab("Isolate")

```

